Polynomial phase estimation by least squares phase unwrapping

### 2013-06-30 paper.tex
added to tables

Tables

\begin{table}[htbp]
\centering
\begin{tabular}{lrrrrr}
 & LSU & CPF & PHAF & HAF & ZW \\ \toprule
$N=99$ &  &  &  &  & \\ 
$N=199$ & 3 & 1 & 3 & 5 & 23 \\ 
$N=299$ &  &  &  & & \\ 
$N=399$ &  &  &  & & \\ 
$N=499$ &  &  &  & & \\ 
$N\to\infty$ & $-\infty$ & ? & ? & 3.77  & ? \\ \bottomrule
\end{tabular}
\caption{Threshold SNR in decibels for estimators with $m=3$}
\label{tablm3}
\end{table}

\begin{table}[htbp]
\centering
\begin{tabular}{lrrrrr}
 & LSU & CPF-HAF & PHAF & HAF & ZW \\ \toprule
$N=99$ &  &  &  &  & \\ 
$N=199$ & 12 & 10 & 12 & 18 & 103 \\ 
$N=299$ &  &  &  & & \\ 
$N=399$ &  &  &  & & \\ 
$N=499$ &  &  &  & & \\ 
$N\to\infty$ & $-\infty$ & $\approx 6.5$ & ?  & 16.6 & ? \\ \bottomrule
\end{tabular}
\caption{Threshold SNR in decibels for estimators with $m=5$}
\label{tablm3}
\end{table}

>>>>

Tables~\ref{tablm3} and~\ref{tablm5} \dots BLERG

\begin{table}[htbp]
\centering
\begin{tabular}{lrrrrr}
 & LSU & CPF & PHAF & HAF & ZW \\ \toprule
$N=49$ &  &  &  &  &  \\ 
$N=99$ & 6 & 3 & 5 & 7 & 27 \\ 
$N=199$ & 3 & 1 & 3 & 5 & 23 \\ 
$N=299$ & 2 & -1 &  & 4 & \\ 
$N\to\infty$ & $-\infty$ & ? & ? & 3.77  & ? \\ \bottomrule
\end{tabular}
\caption{Estimated SNR threshold in decibels with $m=3$}
\label{tablm3}
\end{table}

\begin{table}[htbp]
\centering
\begin{tabular}{lrrrrr}
 & LSU & CPF-HAF & PHAF & HAF & ZW \\ \toprule
$N=49$ &  &  &  & &  \\ 
$N=99$ &  15 &  12 & 13 &  19 & $>100$ \\ 
$N=199$ & 12 & 10 & 12 & 18 & 103 \\ 
$N=299$ &  &  &  & &  \\ 
$N\to\infty$ & $-\infty$ & $\approx 6.5$ & ?  & 16.6 & ? \\ \bottomrule
\end{tabular}
\caption{Estimated SNR threshold in decibels with $m=5$}
\label{tablm5}
\end{table}
